### 2024-06-06 conteudo/background/codeduplication.tex
Add temporary end text for code duplication detection

	\item \textbf{Type-2:} The differences between F and G is the same as the Type-1, with the addition of considering addition and deletion of redudant codes. (ADD FIGURE) shows a typical example of Type-2 Code Duplication \citep{litreview}.

	\item \textbf{Type-3:} The difference between F and G is the same as the Type-2, with the addition of considering the reorder of code blocks as well as statements within code blocks. (ADD FIGURE) shows a typical example of Type-3 Code Duplication \citep{litreview}.

	\item \textbf{Type-4:} The difference between F and G is the same as the Type-3, with the addtionf of considering changes on data sctrucure, the order of operands/operators in expresssions, or replacing part of codes with equivalent composition. (ADD FIGURE) shows a typical example of Type-4 Code Duplication \citep{litreview}. 
\end{itemize}

Given the complexity of  types 3 and 4 of code duplications, the state-of-art approches that aims at this type of
duplication constantly have a high cost in computational time and memory space \citep{litreview}, which is a concern in our research 
that aim to work in large codebases scopes. For this reason we will look after mainly at type 1 and 2 of code duplications.

@@

>>>>

	\item \textbf{Type-2:} The differences between F and G is the same as the type-1, with the addition of considering addition and deletion of redudant codes. (ADD FIGURE) shows a typical example of Type-2 Code Duplication \citep{litreview}.

	\item \textbf{Type-3:} The difference between F and G is the same as the type-2, with the addition of considering the reorder of code blocks as well as statements within code blocks. (ADD FIGURE) shows a typical example of Type-3 Code Duplication \citep{litreview}.

	\item \textbf{Type-4:} The difference between F and G is the same as the type-3, with the addtionf of considering changes on data sctrucure, the order of operands/operators in expresssions, or replacing part of codes with equivalent composition. (ADD FIGURE) shows a typical example of Type-4 Code Duplication \citep{litreview}. 
\end{itemize}

@@

Given the necessity to evaluate and compare approches for code clone detection, it was developed and widely-adopted two datasets: 
OJ-Clone, a dataset collected from a pedagogical online judge system \citep{ojclone}, and BigCloneBench, a datatset collected from over 
25,000 Java software systems \citep{bigclonebench}. The existence of only two spreaded datasets is a open concern in literature as 
the limited scope of OJ-Clone and the problems of BigCloneBench presented by Krinke and Ragkhitwetsagul \citep{bigfail}

The state-of-art methods for code clone detection usually have high computational time and memory space usage, as well being
programming language specific approches, which cannot be easily implemented in programming languagues that were not used in 
their research \citep{litreview}. These are main concern for our research and for this reason we will use a generalist textual-based 
approach based solely on Natural Languague Processing (NLP) text similarity detection methods, which we will introduce and compare
with the literature approches later on this document.
